Comparison of Spatial Partitioning Strategies

### 2025-01-24 paper/paper.tex
Paper: Results section.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.75\textwidth]{even-naive.png}
    \caption{Runtime of naive solution and partitioning strategies.}
    \label{fig:naive}
\end{figure}

@@

% \begin{figure}[h]
%     \centering
%     \includegraphics[width=0.75\textwidth]{even-average.png}
%     \caption{Average runtime of spatial partitioning strategies.}
%     \label{fig:even-average}
% \end{figure}

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{even-naive.png}
    \caption{Runtime of naive solution and partitioning strategies.}
    \label{fig:naive}
\end{figure}

@@

\subsection{Average Runtime}

\subsubsection{Evenly Distributed Objects}
Figure \ref{fig:even-average} shows the average runtime for the program
using the different strategies with an even object distribution. This includes
all other measuring metrics. The X axis describes the amount of objects being
processed. The Y axis describes how much time was spent in milliseconds
executing the particular step in the program.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{even-average.png}
    \caption{Average runtime of spatial partitioning strategies with evenly
    distributed objects.}
    \label{fig:even-average}
\end{figure}

\subsubsection{Unevenly Distributed Objects}
Figure \ref{fig:uneven-average} presents the average runtime for the program
using the different strategies with an uneven object distribution. This includes
all other measuring metrics. As the object count increases the spatial hashing
trends towards a $O(n^2)$ runtime complexity.
\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{uneven-average.png}
    \caption{Average runtime of spatial partitioning strategies with unevenly
    distributed objects.}
    \label{fig:uneven-average}
\end{figure}

\subsection{Insertion}

\subsubsection{Evenly Distributed Objects}
The runtime complexity of the insertion algorithms for evenly distributed
objects is shown in figure \ref{fig:even-insert}.
\begin{figure}[h]
    \centering
    \caption{Average insertion time per object with evenly distributed objects.}
    \includegraphics[width=0.5\textwidth]{even-insert.png}
    \label{fig:even-insert}
\end{figure}

\subsubsection{Unevenly Distributed Objects}
The runtime complexity of the insertion algorithms for evenly distributed
objects is shown in figure \ref{fig:uneven-insert}.
\begin{figure}[h]
    \centering
    \caption{Average insertion time per object with unevenly distributed
    objects.}
    \includegraphics[width=0.5\textwidth]{uneven-insert.png}
    \label{fig:uneven-insert}
\end{figure}

\subsection{Collision}

\subsubsection{Evenly Distributed Objects}
Figure \ref{fig:even-collision} shows the total time spent checking for
colliding objects per iteration with an even distribution. This time also
includes the time taken for querying.
\begin{figure}[h]
    \centering
    \caption{Average collision time for all objects with evenly distributed
    objects.}
    \includegraphics[width=0.5\textwidth]{even-collision.png}
    \label{fig:even-collision}
\end{figure}

\subsubsection{Unevenly Distributed Objects}
Figure \ref{fig:uneven-collision} shows the total time spent checking for
colliding objects per iteration with an uneven distribution. This time also
includes the time taken for querying.
\begin{figure}[h]
    \centering
    \caption{Average collision time for all objects with unevenly distributed
    objects.}
    \includegraphics[width=0.5\textwidth]{uneven-collision.png}
    \label{fig:uneven-collision}
\end{figure}

\subsection{Querying}

\subsubsection{Evenly Distributed Objects}
Figure \ref{fig:even-query} represents the average time taken to query the space
per object with an even distribution.
\begin{figure}[h]
    \centering
    \caption{Average query time per object with evenly distributed objects.}
    \includegraphics[width=0.5\textwidth]{even-query.png}
    \label{fig:even-query}
\end{figure}

\subsubsection{Unevenly Distributed Objects}
Figure \ref{fig:uneven-query} represents the average time taken to query the space
per object with an uneven distribution.
\begin{figure}[h]
    \centering
    \caption{Average query time per object with unevenly distributed objects.}
    \includegraphics[width=0.5\textwidth]{uneven-query.png}
    \label{fig:uneven-query}
\end{figure}
